---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library("externalCov")
library("data.table")
library("stringr")
```

In this vignette we will walk through an example of using the package on summary 
statistics generated using 503 Europeans from 1000G and a reference panel 
of 661 Africans from 1000G. A detailed description of how the data was generated 
can be found in the README file. 

Also included in this package is an annotation file distributed from 1000G. Note 
that it is not in VEP format, and passing this annotation file directly to \texttt{agg_test}
will either cause an error or lead to unexpected behavior. Hence we will read in 
the annotation file in this vignette, and change the columns so that they are in 
VEP format. 

```{r}
anno_file <- "vignetteData/chr2.1000G.NEB.rare_variants.annotation.txt"
df_anno <- fread(anno_file, header = TRUE, data.table = FALSE)
```

Note that there are many columns in the annotation file: 

```{r}
dim(df_anno)
```

Now note that the phenotype was generated using the \textit{NEB} gene on chromosome
2, which has gene boundaries 151485339-151734476. 
